Parsing Postfix log files

### 2009-04-02 doc/logparser-implementation.tex
Added graph showing per-file action invocations. Wrote about action invocation numbers.

XXX RUN test-some, STITCH THE COUNTS OF NUMBER OF RULES INVOKED INTO THE
REAL TIMING DATA, UPDATE THE NUMBER OF INVOCATIONS GRAPH, AND WRITE ABOUT
IT\@.

\parsernames{} actions are described in detail in \sectionref{actions in
detail in implementation}, and \sectionref{adding new actions in
implementation} covers the process of adding a new action.

>>>>

There is no correlation between how often an action is specified by rules
and how often an action is invoked because a rule recognises a log line.
\Graphref{Number of times each action was invoked} shows the number of
times each action was invoked when parsing the \numberOFlogFILES{} log
files used to generate the statistics in \sectionref{parser efficiency}.
The action most commonly specified by rules, \action{DELIVERY\_REJECTED},
is the sixth most commonly invoked, but the second and third most commonly
specified actions are halfway down the list of most commonly invoked
actions, with \action{SAVE\_DATA} being invoked for a mere 0.0903\% of
recognised log lines.

The action invoked most often is \action{MAIL\_QUEUED}; there is only a
0.0051\% difference between it and \action{CLEANUP\_PROCESSING}, and a
further 0.5203\% drop to \action{COMMIT}.  The near equality of these
numbers is to be expected, because every mail delivered by Postfix will be
managed in the queue by \daemon{qmgr} (\action{MAIL\_QUEUED}), processed by
\daemon{cleanup} (\action{CLEANUP\_PROCESSING}), and removed from the queue
by \daemon{qmgr} (\action{COMMIT}); the reason for the small disparity
between \action{MAIL\_QUEUED} and \action{COMMIT} is mainly because mails
are sometimes manually deleted from the queue.  Similarly \action{CONNECT}
and \action{DISCONNECT} have a mere 0.0004\% difference between their
number of invocations, because every connection will have a matching
disconnection unless the \daemon{smtpd} process is killed for some reason.
Unexpectedly there were far fewer connections (\action{CONNECT}) than there
were mails in the queue (\action{MAIL\_QUEUED}); this is because of two
local mail loops (\sectionref{Explaining the peaks in log file size}),
which did not involve delivery via \acronym{SMTP}, and skew the total
numbers.
